---
title: "Top250 IMDB rated TV series"
author: "Alexander Keth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Top250 IMDB rated TV series}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The TV series ratings by series and episode was extracted from [IMDB](http://www.imdb.com) using the [seriespicker](https://github.com/alketh/seriespicker) package available on [github](https://github.com). Due to the time consuming data extraction from [IMDB](http://www.imdb.com) (it takes roughly 3 hours to extract the data) the package comes with a prebuild dataframe called *rating*. Thus, Make sure to install and load the package prior to your data analysis.

```{r, eval = FALSE}
devtools::install_github("alketh/seriespicker")
```

```{r}
library("tibble")
library("seriespicker")
head(rating)
```

## Data extraction

The data was extracted from [IMDB](http://www.imdb.com). As a first step the series ID was read in. See *data-raw/top-series.R* for details. The IDs of the top 250 series are stored as character vector in *ids*.

```{r}
glimpse(ids)
```



## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.cap = "This is the first figure."}
plot(1:10)
```

```{r, fig.cap = "This is the second figure."}
plot(10:1)
```

This is the first footnote^[Very simple footnote.]. This is the second footnote^[Wow, this is really easy.]

